supplmental

### 2020-01-24 paper_stats.Rmd
update after dropping exclusions

To evalaute the possilbity of heterogeneity of treatment effects, we followed the advice of Cortes et al. (REF) and calulated the various outcome variances for the baseline and end-of-period values under the active treatment condtion, and tested wheher the resulting outcome-specific variance ratios were equal to 1 using a two-sided Pitman Morgan test for paired observations (REF). We reported exact p-values from this test.

@@

Heterogenity

>>>>

To evaluate the possibility of heterogeneity of treatment effects, we followed the advice of Cortes et al. (REF) and calculated the various outcome variances for the baseline and end-of-period values under the active treatment condition, and tested whether the resulting outcome-specific variance ratios were equal to 1 using a two-sided Pitman Morgan test for paired observations (REF). We reported exact p-values from this test.

@@

Heterogeneity
